---
title: "CodeBook"
author: "Actin"
date: "May 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting and Cleaning Data Course Project

The cell phone acceleremeter data for this project was obtained from <https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip>.

A number of transformations were performed in order to make the data tidy:

1) The volunteer ID and activity data was merged with the corrsponding oberved values.
2) The test data and training data were merged.
3) The columns were organized to contain one variable per column. In the original dataset, each of the data columns has multiple variables: the domain(time/frequency), the operation applied to the measure (mean/standard deviation), the spatial component (x, y, or z) being reported, or the total magnitude, and the measure observed.
4) The mean of the mean (the overall mean) and the mean of the standard deviation was calculated for each unique combination of subject, activity and the variables listed in item 3 above.

The following is a codebook for the main output:


```{r echo=FALSE, results='asis', message=FALSE, warning=FALSE}
source("run_analysis.R")

require(knitr)

kable(codetable, row.names = F, col.names = c("Variable", "Type", "Description"))

```

